---
title: "ADA-Assignment#1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#ClassWork
# Demo try
```{r}
fVector <- c(12,23,34)
```
#Demo try #2
```{r}
fVector
```

#Matrix
```{r}
m <- matrix(data = c(1,2,3,4),nrow = 2,ncol = 2)
m
m <- matrix(data = c(5,6,7,8),nrow = 2, ncol = 2)

v1 <- c(1,2,3,4)
v2 <- c(6,7,8,9)
m1 <- rbind(v1,v2)
m2 <- cbind(v1,v2)
m1
m2
```
#DataLoad
``` {r}
df<- read.csv("~/Desktop/notWork/School/RWorkingDirectory/88-week-2/students.csv", sep = ",", header = TRUE, stringsAsFactors = FALSE)
df
str(df)
```
#Challenges for Module 4
#Challenge 1
``` {r}
require(stringr)
stringVector <- stringr::str_split("Four score and seven years ago our fathers brought forth on this continent,a new nation, conceived in Liberty , and dedicated to the proposition that all men are created equal"," ")[[1]]
stringVector
stringVector[seq(from = 1,to = length(stringVector), by = 3)]
```

#Challenge 2
###Given the matrix, my_matrix, extract the 2nd, 3rd, and 6th columns and assign them to the variable x
```{r}
my_matrix <- matrix(c(1:80),nrow = 8, ncol = 10)
my_matrix
x<- matrix(c(my_matrix[,2],my_matrix[,6],my_matrix[,9]),nrow = 8,ncol = 3)
x
x <- my_matrix[,c(2,3,6)]
x
```
###Given the matrix, my_matrix, above, extract the 6th to 8th row and assign them to the variable x
```{r}
x<- my_matrix[6:8,]
x
```
###Given the matrix, my_matrix, above, extract the elements from row 2, column 2 to row 6, column 9 and assign them to the variable x
```{r}
x<- my_matrix[c(2:6),c(2:9)]
x
```
#Challenge 3
###Construct a 4-dimensional, 400 element array (5 x 5 x 4 x 4) named *a* consisting of the numbers 400 to 1 (i.e., a descending series)

```{r}
a <- array(data =400:1, dim = c(5, 5, 4, 4))
a
```
### Given this matrix, what would the following return?
``` {r}
a[1, 1, 1, 2]

a[2, 3, 2, ]

a[1:5, 1:5, 3, 3]
```
#Challenge 4
###Create a list representing this (simplified) primate taxonomy. Hint: you can use lists as elements in a list.
```{r}
Platyrrhini <- c ("Cebidae", "Atelidae", "Pitheciidae")
Platyrrhini
Catarrhini <- c ("Cercopithecidae","Hylobatidae","Hominidae")
Catarrhini
Anthropoidea <- list(Platyrrhini,Catarrhini)
Anthropoidea
names(Anthropoidea) <- c("Platyrrhini","Catarrhini")
Anthropoidea
Tarsioidea <- c("Tarsiidae")
Haplorhini <- list(Anthropoidea,Tarsioidea)
names(Haplorhini) <- c("Anthropoidea","Tarsioidea")
Lorisoidea <- c("Lorisidae","Galagidae")
Lemuroidea <- c("Cheirogaleidae","Lepilemuridae","Indriidae","Lemuridae","Daubentoniidae")
Strepsirhini <- list(Lorisoidea,Lemuroidea)
names(Strepsirhini) <- c("Lorisoidea","Lemuroidea")
Strepsirhini
Haplorhini
Primates <- list(Haplorhini,Strepsirhini)
names(Primates) <- c("Haplorhini","Strepsirhini")
Primates
```
#Challenge 5
###Store the following numbers as a 6 x 3 matrix: 3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2
```{r}
challengeF <- matrix(c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2),nrow = 6,ncol = 3)
challengeF
```
###Then, do the following:
####Coerce the matrix to a data frame.
```{r}
str(challengeF)
challengeF <- as.data.frame(challengeF)
str(challengeF)
```
####As a data frame, coerce the second column to be logical-valued
```{r}
challengeF[,2] <- as.logical(challengeF[,2])
str(challengeF)
```
####As a data frame, coerce the third column to be factor-valued
```{r}
challengeF[,3] <- as.factor(challengeF[,3])
str(challengeF)
```
